Algorithm Selection for Graph Algorithms

### 2015-12-16 portfolio/as-graphs.Rnw
some changes to the portfolio stuff

<<echo=FALSE, message=FALSE, warning=FALSE>>=
opts_chunk$set(comment=NA, fig.width='\\textwidth', fig.height=5, fig.pos='!ht')
library(llama)
library(BBmisc)
library(xtable)
library(plyr)
library(aslib)
library(tidyr)

@@

perfs = subset(ldf$data, TRUE, c("instance_id", ldf$performance))
perfs = merge(perfs, vbs.agg, by = "instance_id")
perfs = merge(perfs, pmod, by = "instance_id")
wide = gather_(perfs, "solver", "time", names(perfs)[-1])
wide$type = ifelse(wide$solver %in% c("virtual.best", "portfolio"), "pf", "alg")
ggplot(wide, aes(x = time, col = solver, linetype = type)) + stat_ecdf() +
    scale_linetype_manual(values=c(3,1), guide = FALSE) +
    scale_x_log10(limits = c(10e-5, asscenario$desc$algorithm_cutoff_time)) +
    ylab("fraction of instances solved") +
    geom_vline(xintercept = asscenario$desc$algorithm_cutoff_time, col = "red")
@

@@

perfs = subset(ldf3$data, TRUE, c("instance_id", ldf3$performance))
perfs = merge(perfs, vbs.agg, by = "instance_id")
perfs = merge(perfs, pmod, by = "instance_id")
wide = gather_(perfs, "solver", "time", names(perfs)[-1])
wide$type = ifelse(wide$solver %in% c("virtual.best", "portfolio"), "pf", "alg")
ggplot(wide, aes(x = time, col = solver, linetype = type)) + stat_ecdf() +
    scale_linetype_manual(values=c(3,1), guide = FALSE) +
    scale_x_log10(limits = c(10e-5, asscenario$desc$algorithm_cutoff_time)) +
    ylab("fraction of instances solved") +
    geom_vline(xintercept = asscenario$desc$algorithm_cutoff_time, col = "red")
@

@@

perfs = subset(ldf$data, TRUE, c("instance_id", ldf$performance))
perfs = merge(perfs, vbs.agg, by = "instance_id")
perfs = merge(perfs, pmod, by = "instance_id")
wide = gather_(perfs, "solver", "time", names(perfs)[-1])
wide$type = ifelse(wide$solver %in% c("virtual.best", "portfolio"), "pf", "alg")
ggplot(wide, aes(x = time, col = solver, linetype = type)) + stat_ecdf() +
    scale_linetype_manual(values=c(3,1), guide = FALSE) +
    scale_x_log10(limits = c(10e-5, asscenario$desc$algorithm_cutoff_time)) +
    ylab("fraction of instances solved") +
    geom_vline(xintercept = asscenario$desc$algorithm_cutoff_time, col = "red")
@

@@

perfs = subset(ldf2$data, TRUE, c("instance_id", ldf2$performance))
perfs = merge(perfs, vbs.agg, by = "instance_id")
perfs = merge(perfs, pmod, by = "instance_id")
wide = gather_(perfs, "solver", "time", names(perfs)[-1])
wide$type = ifelse(wide$solver %in% c("virtual.best", "portfolio"), "pf", "alg")
ggplot(wide, aes(x = time, col = solver, linetype = type)) + stat_ecdf() +
    scale_linetype_manual(values=c(3,1), guide = FALSE) +
    scale_x_log10(limits = c(10e-5, asscenario$desc$algorithm_cutoff_time)) +
    ylab("fraction of instances solved") +
    geom_vline(xintercept = asscenario$desc$algorithm_cutoff_time, col = "red")
@

@@

perfs = subset(ldf$data, TRUE, c("instance_id", ldf$performance))
perfs = merge(perfs, vbs.agg, by = "instance_id")
perfs = merge(perfs, pmod, by = "instance_id")
wide = gather_(perfs, "solver", "time", names(perfs)[-1])
wide$type = ifelse(wide$solver %in% c("virtual.best", "portfolio"), "pf", "alg")
ggplot(wide, aes(x = time, col = solver, linetype = type)) + stat_ecdf() +
    scale_linetype_manual(values=c(3,1), guide = FALSE) +
    scale_x_log10(limits = c(10e-5, asscenario$desc$algorithm_cutoff_time)) +
    ylab("fraction of instances solved") +
    geom_vline(xintercept = asscenario$desc$algorithm_cutoff_time, col = "red")
@

>>>>

<<echo=FALSE, message=FALSE, warning=FALSE>>=
opts_chunk$set(comment=NA, fig.width='\\textwidth', fig.height=5, fig.pos='!ht')
library(llama)
library(BBmisc)
library(xtable)
library(plyr)
library(aslib)
library(tidyr)
library(ggthemes)
library(grid)
library(scales)

@@

perfs = subset(ldf$data, TRUE, c("instance_id", ldf$performance))
perfs = merge(perfs, vbs.agg, by = "instance_id")
perfs = merge(perfs, pmod, by = "instance_id")
wide = gather_(perfs, "solver", "time", names(perfs)[-1])
wide$type = ifelse(wide$solver %in% c("virtual.best", "portfolio"), "pf", "alg")
write.csv(wide, file = "all.csv", row.names = FALSE)

p.full = ggplot(wide, aes(x = time, col = solver, linetype = type)) +
    stat_ecdf() +
    scale_linetype_manual(values=c(3,1), guide = FALSE) +
    scale_x_log10(breaks = trans_breaks("log10", function(x) 10^x, n = 10),
                  labels = trans_format("log10", math_format(10^.x)),
                  limits = c(1, asscenario$desc$algorithm_cutoff_time-1)) +
    coord_cartesian(xlim = c(1, asscenario$desc$algorithm_cutoff_time-1),
        ylim = c(0,1)) +
    ylab("fraction of instances solved") + xlab("time [ms]") +
    annotation_logticks(sides = "b") +
    theme_tufte(base_family='Times', base_size = 14) +
    guides(col = guide_legend(ncol = 2, keyheight = .8)) +
    theme(legend.justification=c(1,0), legend.position=c(1,0.5), aspect.ratio = 0.6, axis.line = element_line(colour="black"), panel.grid = element_line(), panel.grid.major = element_line(colour="lightgray"))

p.zoom = ggplot(wide, aes(x = time, col = solver, linetype = type)) +
    stat_ecdf() +
    scale_linetype_manual(values=c(3,1), guide = FALSE) +
    scale_x_log10(breaks = trans_breaks("log10", function(x) 10^x, n = 3),
                  labels = trans_format("log10", math_format(10^.x)),
                  limits = c(1, asscenario$desc$algorithm_cutoff_time-1)) +
    coord_cartesian(xlim = c(asscenario$desc$algorithm_cutoff_time/10, asscenario$desc$algorithm_cutoff_time-1),
        ylim = c(.95,1)) +
    annotation_logticks(sides = "b") +
    theme_tufte(base_family='Times', base_size = 14) +
    theme(legend.position="none",
        axis.title.x=element_blank(), axis.title.y=element_blank(),
        panel.background = element_rect(fill='white', colour = "white"),
        axis.line = element_line(colour="black"),
        panel.grid = element_line(),
        panel.grid.major = element_line(colour="lightgray"))
vp = viewport(width = 0.5, height = 0.3, x = 0.7, y = 0.42)
print(p.full)
print(p.zoom, vp = vp)
@

@@

perfs = subset(ldf3$data, TRUE, c("instance_id", ldf3$performance))
perfs = merge(perfs, vbs.agg, by = "instance_id")
perfs = merge(perfs, pmod, by = "instance_id")
wide = gather_(perfs, "solver", "time", names(perfs)[-1])
wide$type = ifelse(wide$solver %in% c("virtual.best", "portfolio"), "pf", "alg")
write.csv(wide, file = "no-presolved.csv", row.names = FALSE)
p.full = ggplot(wide, aes(x = time, col = solver, linetype = type)) +
    stat_ecdf() +
    scale_linetype_manual(values=c(3,1), guide = FALSE) +
    scale_x_log10(breaks = trans_breaks("log10", function(x) 10^x, n = 10),
                  labels = trans_format("log10", math_format(10^.x)),
                  limits = c(1, asscenario$desc$algorithm_cutoff_time-1)) +
    coord_cartesian(xlim = c(1, asscenario$desc$algorithm_cutoff_time-1),
        ylim = c(0,1)) +
    ylab("fraction of instances solved") + xlab("time [ms]") +
    annotation_logticks(sides = "b") +
    theme_tufte(base_family='Times', base_size = 14) +
    guides(col = guide_legend(ncol = 2, keyheight = .8)) +
    theme(legend.justification=c(1,0), legend.position=c(1,0.5), aspect.ratio = 0.6, axis.line = element_line(colour="black"), panel.grid = element_line(), panel.grid.major = element_line(colour="lightgray"))

p.zoom = ggplot(wide, aes(x = time, col = solver, linetype = type)) +
    stat_ecdf() +
    scale_linetype_manual(values=c(3,1), guide = FALSE) +
    scale_x_log10(breaks = trans_breaks("log10", function(x) 10^x, n = 3),
                  labels = trans_format("log10", math_format(10^.x)),
                  limits = c(1, asscenario$desc$algorithm_cutoff_time-1)) +
    coord_cartesian(xlim = c(asscenario$desc$algorithm_cutoff_time/10, asscenario$desc$algorithm_cutoff_time-1),
        ylim = c(.95,1)) +
    annotation_logticks(sides = "b") +
    theme_tufte(base_family='Times', base_size = 14) +
    theme(legend.position="none",
        axis.title.x=element_blank(), axis.title.y=element_blank(),
        panel.background = element_rect(fill='white', colour = "white"),
        axis.line = element_line(colour="black"),
        panel.grid = element_line(),
        panel.grid.major = element_line(colour="lightgray"))
vp = viewport(width = 0.5, height = 0.3, x = 0.7, y = 0.42)
print(p.full)
print(p.zoom, vp = vp)
@

@@

perfs = subset(ldf$data, TRUE, c("instance_id", ldf$performance))
perfs = merge(perfs, vbs.agg, by = "instance_id")
perfs = merge(perfs, pmod, by = "instance_id")
wide = gather_(perfs, "solver", "time", names(perfs)[-1])
wide$type = ifelse(wide$solver %in% c("virtual.best", "portfolio"), "pf", "alg")
write.csv(wide, file = "no-presolved-allinstances.csv", row.names = FALSE)
p.full = ggplot(wide, aes(x = time, col = solver, linetype = type)) +
    stat_ecdf() +
    scale_linetype_manual(values=c(3,1), guide = FALSE) +
    scale_x_log10(breaks = trans_breaks("log10", function(x) 10^x, n = 10),
                  labels = trans_format("log10", math_format(10^.x)),
                  limits = c(1, asscenario$desc$algorithm_cutoff_time-1)) +
    coord_cartesian(xlim = c(1, asscenario$desc$algorithm_cutoff_time-1),
        ylim = c(0,1)) +
    ylab("fraction of instances solved") + xlab("time [ms]") +
    annotation_logticks(sides = "b") +
    theme_tufte(base_family='Times', base_size = 14) +
    guides(col = guide_legend(ncol = 2, keyheight = .8)) +
    theme(legend.justification=c(1,0), legend.position=c(1,0.5), aspect.ratio = 0.6, axis.line = element_line(colour="black"), panel.grid = element_line(), panel.grid.major = element_line(colour="lightgray"))

p.zoom = ggplot(wide, aes(x = time, col = solver, linetype = type)) +
    stat_ecdf() +
    scale_linetype_manual(values=c(3,1), guide = FALSE) +
    scale_x_log10(breaks = trans_breaks("log10", function(x) 10^x, n = 3),
                  labels = trans_format("log10", math_format(10^.x)),
                  limits = c(1, asscenario$desc$algorithm_cutoff_time-1)) +
    coord_cartesian(xlim = c(asscenario$desc$algorithm_cutoff_time/10, asscenario$desc$algorithm_cutoff_time-1),
        ylim = c(.95,1)) +
    annotation_logticks(sides = "b") +
    theme_tufte(base_family='Times', base_size = 14) +
    theme(legend.position="none",
        axis.title.x=element_blank(), axis.title.y=element_blank(),
        panel.background = element_rect(fill='white', colour = "white"),
        axis.line = element_line(colour="black"),
        panel.grid = element_line(),
        panel.grid.major = element_line(colour="lightgray"))
vp = viewport(width = 0.5, height = 0.3, x = 0.7, y = 0.42)
print(p.full)
print(p.zoom, vp = vp)
@

@@

perfs = subset(ldf2$data, TRUE, c("instance_id", ldf2$performance))
perfs = merge(perfs, vbs.agg, by = "instance_id")
perfs = merge(perfs, pmod, by = "instance_id")
wide = gather_(perfs, "solver", "time", names(perfs)[-1])
wide$type = ifelse(wide$solver %in% c("virtual.best", "portfolio"), "pf", "alg")
write.csv(wide, file = "no-presolved-presolver.csv", row.names = FALSE)
p.full = ggplot(wide, aes(x = time, col = solver, linetype = type)) +
    stat_ecdf() +
    scale_linetype_manual(values=c(3,1), guide = FALSE) +
    scale_x_log10(breaks = trans_breaks("log10", function(x) 10^x, n = 10),
                  labels = trans_format("log10", math_format(10^.x)),
                  limits = c(1, asscenario$desc$algorithm_cutoff_time-1)) +
    coord_cartesian(xlim = c(1, asscenario$desc$algorithm_cutoff_time-1),
        ylim = c(0,1)) +
    ylab("fraction of instances solved") + xlab("time [ms]") +
    annotation_logticks(sides = "b") +
    theme_tufte(base_family='Times', base_size = 14) +
    guides(col = guide_legend(ncol = 2, keyheight = .8)) +
    theme(legend.justification=c(1,0), legend.position=c(1,0.5), aspect.ratio = 0.6, axis.line = element_line(colour="black"), panel.grid = element_line(), panel.grid.major = element_line(colour="lightgray"))

p.zoom = ggplot(wide, aes(x = time, col = solver, linetype = type)) +
    stat_ecdf() +
    scale_linetype_manual(values=c(3,1), guide = FALSE) +
    scale_x_log10(breaks = trans_breaks("log10", function(x) 10^x, n = 3),
                  labels = trans_format("log10", math_format(10^.x)),
                  limits = c(1, asscenario$desc$algorithm_cutoff_time-1)) +
    coord_cartesian(xlim = c(asscenario$desc$algorithm_cutoff_time/10, asscenario$desc$algorithm_cutoff_time-1),
        ylim = c(.95,1)) +
    annotation_logticks(sides = "b") +
    theme_tufte(base_family='Times', base_size = 14) +
    theme(legend.position="none",
        axis.title.x=element_blank(), axis.title.y=element_blank(),
        panel.background = element_rect(fill='white', colour = "white"),
        axis.line = element_line(colour="black"),
        panel.grid = element_line(),
        panel.grid.major = element_line(colour="lightgray"))
vp = viewport(width = 0.5, height = 0.3, x = 0.7, y = 0.42)
print(p.full)
print(p.zoom, vp = vp)
@

@@

perfs = subset(ldf$data, TRUE, c("instance_id", ldf$performance))
perfs = merge(perfs, vbs.agg, by = "instance_id")
perfs = merge(perfs, pmod, by = "instance_id")
wide = gather_(perfs, "solver", "time", names(perfs)[-1])
wide$type = ifelse(wide$solver %in% c("virtual.best", "portfolio"), "pf", "alg")
write.csv(wide, file = "no-presolved-presolver-allinstances.csv", row.names = FALSE)
p.full = ggplot(wide, aes(x = time, col = solver, linetype = type)) +
    stat_ecdf() +
    scale_linetype_manual(values=c(3,1), guide = FALSE) +
    scale_x_log10(breaks = trans_breaks("log10", function(x) 10^x, n = 10),
                  labels = trans_format("log10", math_format(10^.x)),
                  limits = c(1, asscenario$desc$algorithm_cutoff_time-1)) +
    coord_cartesian(xlim = c(1, asscenario$desc$algorithm_cutoff_time-1),
        ylim = c(0,1)) +
    ylab("fraction of instances solved") + xlab("time [ms]") +
    annotation_logticks(sides = "b") +
    theme_tufte(base_family='Times', base_size = 14) +
    guides(col = guide_legend(ncol = 2, keyheight = .8)) +
    theme(legend.justification=c(1,0), legend.position=c(1,0.5), aspect.ratio = 0.6, axis.line = element_line(colour="black"), panel.grid = element_line(), panel.grid.major = element_line(colour="lightgray"))

p.zoom = ggplot(wide, aes(x = time, col = solver, linetype = type)) +
    stat_ecdf() +
    scale_linetype_manual(values=c(3,1), guide = FALSE) +
    scale_x_log10(breaks = trans_breaks("log10", function(x) 10^x, n = 3),
                  labels = trans_format("log10", math_format(10^.x)),
                  limits = c(1, asscenario$desc$algorithm_cutoff_time-1)) +
    coord_cartesian(xlim = c(asscenario$desc$algorithm_cutoff_time/10, asscenario$desc$algorithm_cutoff_time-1),
        ylim = c(.95,1)) +
    annotation_logticks(sides = "b") +
    theme_tufte(base_family='Times', base_size = 14) +
    theme(legend.position="none",
        axis.title.x=element_blank(), axis.title.y=element_blank(),
        panel.background = element_rect(fill='white', colour = "white"),
        axis.line = element_line(colour="black"),
        panel.grid = element_line(),
        panel.grid.major = element_line(colour="lightgray"))
vp = viewport(width = 0.5, height = 0.3, x = 0.7, y = 0.42)
print(p.full)
print(p.zoom, vp = vp)
@

%\subsection*{Only Glasgow variants}
%
%<<echo=FALSE, results='asis', warning=FALSE, message=FALSE>>=
%ldf.glasgow = ldf2
%ldf.glasgow$performance = c("glasgow1", "glasgow2", "glasgow3", "glasgow4")
%ldf.glasgow$success = c("glasgow1_success", "glasgow2_success", "glasgow3_success", "glasgow4_success")
%
%pnames = ldf.glasgow$performance
%snames = ldf.glasgow$success
%optfun = min
%best = apply(ldf.glasgow$data, 1,
%    function(x) {
%        tosel = pnames
%        nosuccs = sapply(snames[which(as.logical(x[snames]) == FALSE)], function(y) { unlist(strsplit(y, "_"))[1] })
%        tosel = setdiff(pnames, nosuccs)
%        if(length(tosel) == 0) {
%            # nothing was able to solve this instance
%            return(NA)
%        } else {
%            perfs = as.numeric(x[tosel])
%            return(tosel[which(perfs == optfun(perfs))])
%        }
%    })
%# simplify...
%names(best) = NULL
%ldf.glasgow$best = best
%
%resvbs = data.frame(model = "virtual best",
%    mean.misclassification.penalty = mean(misclassificationPenalties(ldf.glasgow, vbs)),
%    solved = sum(successes(ldf.glasgow, vbs)),
%    mean.performance = mean(parscores(ldf.glasgow, vbs, factor = 1)),
%    median.performance = median(parscores(ldf.glasgow, vbs, factor = 1)))
%ressb = data.frame(model = "single best",
%    mean.misclassification.penalty = mean(misclassificationPenalties(ldf.glasgow, singleBest)),
%    solved = sum(successes(ldf.glasgow, singleBest)),
%    mean.performance = mean(parscores(ldf.glasgow, singleBest, factor = 1)),
%    median.performance = median(parscores(ldf.glasgow, singleBest, factor = 1)))
%
%modelc = classify(rflearner, ldf.glasgow)
%resc = data.frame(model = "classification",
%    mean.misclassification.penalty = mean(misclassificationPenalties(ldf.glasgow, modelc)),
%    solved = sum(successes(ldf.glasgow, modelc)),
%    mean.performance = mean(parscores(ldf.glasgow, modelc, factor = 1)),
%    median.performance = median(parscores(ldf.glasgow, modelc, factor = 1)))
%times = sapply(modelc$models, function(x) row.names(sortByCol(as.data.frame(x$learner.model$importance), "MeanDecreaseGini", asc = FALSE))[1])
%print(xtable(as.table(sort(table(times), decreasing = TRUE)), caption = "Most important features for classification."), booktabs = TRUE)
%
%modelr = regression(makeLearner("regr.randomForest"), ldf.glasgow)
%resr = data.frame(model = "regression",
%    mean.misclassification.penalty = mean(misclassificationPenalties(ldf.glasgow, modelr)),
%    solved = sum(successes(ldf.glasgow, modelr)),
%    mean.performance = mean(parscores(ldf.glasgow, modelr, factor = 1)),
%    median.performance = median(parscores(ldf.glasgow, modelr, factor = 1)))
%times = sapply(modelr$models, function(x) row.names(sortByCol(as.data.frame(x$learner.model$importance), "IncNodePurity", asc = FALSE))[1])
%print(xtable(as.table(sort(table(times), decreasing = TRUE)), caption = "Most important features for regression."), booktabs = TRUE)
%
%modelcp = classifyPairs(rflearner, ldf.glasgow)
%rescp = data.frame(model = "classifyPairs",
%    mean.misclassification.penalty = mean(misclassificationPenalties(ldf.glasgow, modelcp)),
%    solved = sum(successes(ldf.glasgow, modelcp)),
%    mean.performance = mean(parscores(ldf.glasgow, modelcp, factor = 1)),
%    median.performance = median(parscores(ldf.glasgow, modelcp, factor = 1)))
%times = sapply(modelcp$models, function(x) row.names(sortByCol(as.data.frame(x$learner.model$importance), "MeanDecreaseGini", asc = FALSE))[1])
%print(xtable(as.table(sort(table(times), decreasing = TRUE)), caption = "Most important features for classificationPairs."), booktabs = TRUE)
%
%modelrp = regressionPairs(makeLearner("regr.randomForest"), ldf.glasgow)
%resrp = data.frame(model = "regressionPairs",
%    mean.misclassification.penalty = mean(misclassificationPenalties(ldf.glasgow, modelrp)),
%    solved = sum(successes(ldf.glasgow, modelrp)),
%    mean.performance = mean(parscores(ldf.glasgow, modelrp, factor = 1)),
%    median.performance = median(parscores(ldf.glasgow, modelrp, factor = 1)))
%times = sapply(modelrp$models, function(x) row.names(sortByCol(as.data.frame(x$learner.model$importance), "IncNodePurity", asc = FALSE))[1])
%print(xtable(as.table(sort(table(times), decreasing = TRUE)), caption = "Most important features for regressionPairs."), booktabs = TRUE)
%
%tab = rbind(resvbs, ressb, resc, resr, rescp, resrp)
%print(xtable(tab, digits = 0, caption = "Preliminary algorithm selection results with presolver for Glasgow solvers."), booktabs = TRUE, include.rownames = FALSE)
%@
%
%<<echo=FALSE,fig.cap='ECDF for algorithms and portfolio (best model).'>>=
%vbs.agg = aggregate(as.formula(paste("score~", paste(c("instance_id", "iteration"), sep="+", collapse="+"))), vbs(ldf.glasgow), function(ss) { ss[1] })
%vbs.agg$virtual.best = parscores(ldf.glasgow, vbs, factor = 1)
%vbs.agg$iteration = NULL
%vbs.agg$score = NULL
%
%pmod = data.frame(instance_id = unique(mod$predictions$instance_id), portfolio = parscores(ldf.glasgow, mod, factor = 1))
%
%perfs = subset(ldf.glasgow$data, TRUE, c("instance_id", ldf.glasgow$performance))
%perfs = merge(perfs, vbs.agg, by = "instance_id")
%perfs = merge(perfs, pmod, by = "instance_id")
%wide = gather_(perfs, "solver", "time", names(perfs)[-1])
%wide$type = ifelse(wide$solver %in% c("virtual.best", "portfolio"), "pf", "alg")
%ggplot(wide, aes(x = time, col = solver, linetype = type)) + stat_ecdf() +
%    scale_linetype_manual(values=c(3,1), guide = FALSE) +
%    scale_x_log10(breaks = trans_breaks("log10", function(x) 10^x, n = 10),
%                  labels = trans_format("log10", math_format(10^.x)),
%                  limits = c(1, asscenario$desc$algorithm_cutoff_time-1)) +
%    coord_cartesian(xlim = c(1, asscenario$desc$algorithm_cutoff_time-1),
%        ylim = c(0,1)) +
%    ylab("fraction of instances solved") + xlab("time [ms]") +
%    annotation_logticks(sides = "b") +
%    theme_tufte(base_family='sans', base_size = 12) +
%    theme(legend.justification=c(1,0), legend.position=c(1,0.1), aspect.ratio = 0.6, axis.line = element_line(colour="black"), panel.grid = element_line(), panel.grid.major = element_line(colour="lightgray"))
%@
%
%<<echo=FALSE,fig.cap='ECDF for algorithms and portfolio for all instances (best model).'>>=
%vbs.agg = aggregate(as.formula(paste("score~", paste(c("instance_id", "iteration"), sep="+", collapse="+"))), vbs(ldf), function(ss) { ss[1] })
%vbs.agg$virtual.best = parscores(ldf, vbs, factor = 1)
%vbs.agg$iteration = NULL
%vbs.agg$score = NULL
%
%pmod = data.frame(instance_id = unique(mod$predictions$instance_id), portfolio = parscores(ldf.glasgow, mod, factor = 1))
%pmod = rbind(pmod, data.frame(instance_id = factor(presolved), portfolio = subset(ldf$data, ldf$data$instance_id %in% presolved)$lad_features))
%vf2pre = setdiff(ldf3$data$instance_id, ldf.glasgow$data$instance_id)
%pmod = rbind(pmod, data.frame(instance_id = factor(vf2pre), portfolio = subset(ldf$data, ldf$data$instance_id %in% vf2pre)$vf2))
%
%perfs = subset(ldf$data, TRUE, c("instance_id", ldf$performance))
%perfs = merge(perfs, vbs.agg, by = "instance_id")
%perfs = merge(perfs, pmod, by = "instance_id")
%wide = gather_(perfs, "solver", "time", names(perfs)[-1])
%wide$type = ifelse(wide$solver %in% c("virtual.best", "portfolio"), "pf", "alg")
%ggplot(wide, aes(x = time, col = solver, linetype = type)) + stat_ecdf() +
%    scale_linetype_manual(values=c(3,1), guide = FALSE) +
%    scale_x_log10(breaks = trans_breaks("log10", function(x) 10^x, n = 10),
%                  labels = trans_format("log10", math_format(10^.x)),
%                  limits = c(1, asscenario$desc$algorithm_cutoff_time-1)) +
%    coord_cartesian(xlim = c(1, asscenario$desc$algorithm_cutoff_time-1),
%        ylim = c(0,1)) +
%    ylab("fraction of instances solved") + xlab("time [ms]") +
%    annotation_logticks(sides = "b") +
%    theme_tufte(base_family='sans', base_size = 12) +
%    theme(legend.justification=c(1,0), legend.position=c(1,0.1), aspect.ratio = 0.6, axis.line = element_line(colour="black"), panel.grid = element_line(), panel.grid.major = element_line(colour="lightgray"))
%@
%
%\clearpage

%\section*{Different timeouts}
%
%Consider timeouts $10^2$\ldots$10^8$ (after filtering and presolving).
%
%<<echo=FALSE, results='asis', warning=FALSE, message=FALSE>>=
%timeoutExps = 2:8
%
%tab = rbind.fill(lapply(timeoutExps, function(to) {
%    ldf.tmp = ldf2
%    if(10^to < asscenario$desc$algorithm_cutoff_time) {
%        for(p in ldf.tmp$performance) {
%            ldf.tmp$data[paste0(p, "_success")] = sapply(ldf.tmp$data[,p], function(x) x <= 10^to)
%            ldf.tmp$data[p] = sapply(ldf.tmp$data[,p], function(x) min(x, 10^to))
%        }
%        pnames = ldf.tmp$performance
%        snames = ldf.tmp$success
%        optfun = min
%        best = apply(ldf.tmp$data, 1,
%            function(x) {
%                tosel = pnames
%                nosuccs = sapply(snames[which(as.logical(x[snames]) == FALSE)], function(y) { unlist(strsplit(y, "_"))[1] })
%                tosel = setdiff(pnames, nosuccs)
%                if(length(tosel) == 0) {
%                    # nothing was able to solve this instance
%                    return(NA)
%                } else {
%                    perfs = as.numeric(x[tosel])
%                    return(tosel[which(perfs == optfun(perfs))])
%                }
%            })
%        names(best) = NULL
%        ldf.tmp$best = best
%    }
%    ldf.tmp$train = NULL
%    ldf.tmp$test = NULL
%    ldf.tmp = cvFolds(ldf.tmp)
%
%    resvbs = data.frame(model = "virtual best",
%        mean.misclassification.penalty = mean(misclassificationPenalties(ldf.tmp, vbs)),
%        solved = sum(successes(ldf.tmp, vbs)),
%        mean.performance = mean(parscores(ldf.tmp, vbs, factor = 1)),
%        median.performance = median(parscores(ldf.tmp, vbs, factor = 1)))
%    ressb = data.frame(model = "single best",
%        mean.misclassification.penalty = mean(misclassificationPenalties(ldf.tmp, singleBest)),
%        solved = sum(successes(ldf.tmp, singleBest)),
%        mean.performance = mean(parscores(ldf.tmp, singleBest, factor = 1)),
%        median.performance = median(parscores(ldf.tmp, singleBest, factor = 1)))
%
%    modelc = classify(rflearner, ldf.tmp)
%    resc = data.frame(model = "classification",
%        mean.misclassification.penalty = mean(misclassificationPenalties(ldf.tmp, modelc)),
%        solved = sum(successes(ldf.tmp, modelc)),
%        mean.performance = mean(parscores(ldf.tmp, modelc, factor = 1)),
%        median.performance = median(parscores(ldf.tmp, modelc, factor = 1)))
%
%    modelr = regression(makeLearner("regr.randomForest"), ldf.tmp)
%    resr = data.frame(model = "regression",
%        mean.misclassification.penalty = mean(misclassificationPenalties(ldf.tmp, modelr)),
%        solved = sum(successes(ldf.tmp, modelr)),
%        mean.performance = mean(parscores(ldf.tmp, modelr, factor = 1)),
%        median.performance = median(parscores(ldf.tmp, modelr, factor = 1)))
%
%    modelcp = classifyPairs(rflearner, ldf.tmp)
%    rescp = data.frame(model = "classifyPairs",
%        mean.misclassification.penalty = mean(misclassificationPenalties(ldf.tmp, modelcp)),
%        solved = sum(successes(ldf.tmp, modelcp)),
%        mean.performance = mean(parscores(ldf.tmp, modelcp, factor = 1)),
%        median.performance = median(parscores(ldf.tmp, modelcp, factor = 1)))
%
%    modelrp = regressionPairs(makeLearner("regr.randomForest"), ldf.tmp)
%    resrp = data.frame(model = "regressionPairs",
%        mean.misclassification.penalty = mean(misclassificationPenalties(ldf.tmp, modelrp)),
%        solved = sum(successes(ldf.tmp, modelrp)),
%        mean.performance = mean(parscores(ldf.tmp, modelrp, factor = 1)),
%        median.performance = median(parscores(ldf.tmp, modelrp, factor = 1)))
%
%    sb = levels(singleBest(ldf.tmp)$algorithm)
%    cbind(data.frame(timeout = 10^to, single.best = sb), rbind(resvbs, ressb, resc, resr, rescp, resrp))
%}))
%
%print(xtable(tab, digits = 0, caption = "Preliminary algorithm selection results for different timeouts with presolver."), booktabs = TRUE, include.rownames = FALSE)
%@
